Simulating an Interplanetary Internet

### 2024-04-10 paper/paper.tex
added udp stuff
add UDP analysis

We believe that UDP sends a large number of messages at the start that are all queued, processed, and sent. After those messages are sent, the next batch is prepared immediately. This curve could be caused by the queuing delay from the large number of messages that are sent. UDP does not wait for messages to be received and will therefore create a large backlog which slows everything down when dequeuing messages.

>>>>

The message size is the same across all of the messages. This makes sense as the message size do not need to be different across different messages. This is different compared to TCP and New Reno.

On the left side of the graph before approximately $t = 25000$ this is where
the planet most likely has a direct path between Earth and Mars. This has a
steady pattern of a batch of messages are queued, they are sent, and after they
are sent the next batch of messages are queued, and calculated the propagation
delay at the time that it is queued. This leads to the clusters which can be seen.
The curvature of the delay is most likely attributed to the movement of Earth
relative to Mars, that is that they are getting closer together. Queueing delay is likely small in this section suggested by the tight groupings.

At approximately time $t = 25000$ the direct path between Earth and Mars is
blocked. This means that the messages have to be routed through a secondary
satellite. The vertical gap between the horizontal lines is roughly 0.001
seconds. This is the same time as it takes for a message to take for a message
to send between Earth and the ISS and similarly between Mars and the Mars
Orbiter. The reason for the multiple horizontal lines is that messages may be
passed several times between the planet and its satellite before it is finally
delivered across the large propagation delay between the planets Earth and Mars.
The propagation delay could be seen through the length of the horizontal lines.
This is representative of the time it takes to clear each batch when it is sent.
Once an entire batch is sent it will re-calculate the propagation delay which
will then be represented in new different horizontal lines. The long lines show
that there was a large spike in queuing delay as the topology changed which
became smaller as it cleared. The curvature of this curve likely represents the
change in the relative distance between the satellites orbiting Earth and Mars
becoming further apart. This is clear here due to the extremely small variation
in propagation delay.

This analysis cannot be 100\% verified due to the data mined from NS-3 did not give a ton of information about the messages which were sent on our simulated network.
